Paper Analysis

### 2025-02-13 Paper_WriteUp/Paper_Plots.qmd

```{r figure s4 left - plot player effects}
#| eval: false
indiv_plot_17_19 <- player_pars |> 
  filter(param == 1) |> 
  ggplot(aes(y = reorder(player_name, value, FUN = median), x = value)) +
  stat_histinterval() +
  labs(x = "Estimated Player Effect", y = element_blank()) +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

@@

## then need to overlay the true values also
true_values <- fit_gm_bullet_prev$summary() |> 
  filter(variable %in% c("mu_beta", "gamma1", "gamma2")) |> 
  select(variable, mean)

perm_gm_global <- sim_pars |> 
  filter(variable %in% c("mu_beta",  "gamma1", "gamma2",
                           "sigma_1", "tau[1]", "tau[2]",
                           "sigma_g1", "sigma_g2")) |> 
  ggplot(aes(mean)) +
  geom_histogram() +
  facet_wrap(~variable, scales = "free") +
  geom_vline(data = true_values, mapping = aes(xintercept = mean),
             col = "red") +
  theme_3col() +
  labs(x = element_blank(), y = element_blank())

@@

perm_gm_winner <- player_pars |> 
  filter(param == 2) |>
  mutate(y = factor(player_name, levels = levels)) |> 
  ggplot(aes(x = mean, y = y)) +
  stat_histinterval(slab_fill = NA, .width = c(0.5, 0.95)) +
  geom_segment(data = true_vals, 
               aes(x = mean, y = y, yend = yend), col = "red") +
  theme_single_y() +
  labs(x = "Estimated W/L-Effect", y = "")

>>>>

```{r figure s4 left - plot player effects}
#| eval: false
indiv_plot_17_19 <- player_pars |> 
  filter(param == 1) |> 
  ggplot(aes(y = reorder(player_name, value, FUN = median), x = value)) +
  stat_histinterval() +
  labs(x = "Estimated Player Effect", y = element_blank(),
       title = "1700-1900 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

@@

## then need to overlay the true values also
true_values <- fit_gm_bullet_prev$summary() |> 
  dplyr::filter(variable %in% c("mu_beta", "gamma1", "gamma2")) |> 
  select(variable, mean)

perm_gm_global <- sim_pars |> 
  dplyr::filter(variable %in% c("mu_beta",  "gamma1", "gamma2")) |> 
  ggplot(aes(mean)) +
  geom_histogram() +
  facet_wrap(~variable, scales = "free") +
  geom_vline(data = true_values, mapping = aes(xintercept = mean),
             col = "red") +
  theme_3col() +
  labs(x = element_blank(), y = element_blank())

@@

true_vals <- true_beta |> 
  filter(param == 2) |>  
  mutate(y = factor(player_name, levels = levels)) |> 
  arrange(y) |> 
  mutate(y_fake = row_number() - 0.25,
         yend = row_number() + 0.25)

perm_gm_winner <- player_pars |> 
  filter(param == 2) |>
  mutate(y = factor(player_name, levels = levels)) |> 
  ggplot(aes(x = mean, y = y)) +
  stat_histinterval(slab_fill = NA, .width = c(0.5, 0.95)) +
  geom_segment(data = true_vals,
               aes(x = mean, y = y_fake, yend = yend), col = "red") +
  theme_single_y() +
  labs(x = "Estimated W/L-Effect", y = "")
